\documentclass[aspectratio=169]{beamer}
\usepackage{helvet}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{Ilmenau}

\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}

\usepackage{units}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fixmath}
%\usepackage{pgfmath}
\usepackage{wrapfig}


\title{Stories around ModBus}
\subtitle{Why Modbus Is Even Worse than SNMP}
\author{Richard Hartmann,\\
RichiH@\{freenode,OFTC,IRCnet\},\\
richih@\{debian,fosdem,richih\}.org,\\
@TwitchiH}
\date{2020-02-02}


\begin{document}



\section{Introduction}


\subsection{}

\begin{frame}
	\titlepage
\end{frame}

%\begin{frame}
%	\frametitle{whoami}
%	\begin{itemize}
%		\item Richard "RichiH" Hartmann
%		\item Community Director at Grafana
%		\item Project lead for building one of the most modern datacenters in Europe
%		\begin{itemize}
%			\item First one world-wide to be certified under the new revision of EN 50600
%			\item One of less than a dozen with both security and availability class 4
%			\item There's no harsher non-military standard on Earth
%		\end{itemize}
%		\item FOSDEM, DENOGx, PromCon staff
%		\item Prometheus team member
%	\end{itemize}
%\end{frame}

\begin{frame}
	\frametitle{Show of hands}
	\begin{itemize}
		\item Who is running directly on or dealing with hardware?
		\item Who has heard of SNMP?
		\item Who has heard of Modbus?
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Show of hands}
	\begin{itemize}
		\item Who likes SNMP?
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Modbus}
	\centering
	\vfill
	Modbus is worse
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Relation}
	\begin{itemize}
		\item SNMPv1: 1988
		\item Modbus release: 1979 (!)
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{SNMP}
	\centering
	\vfill
	Without SNMP, the Internet would break down within hours
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Modbus}
	\centering
	\vfill
	Without Modbus, society would break down within hours
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Modbus}
	\begin{itemize}
		\item Without Modbus, you would have no power
		\item Without Modbus, you would have no water
		\item Without Modbus, you would have no ports
		\item Without Modbus, you would have no medicine
		\item Without Modbus, you would have no processed food
		\item Without Modbus, you would have no clothes
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Modbus}
	\centering
	\vfill
	So, of course, Modbus has zero security built in
	\vfill
\end{frame}


\section{Background}


\subsection{}

\begin{frame}
	\frametitle{Flavours of Modbus}
	\begin{itemize}
		\item Modbus RTU: Serial bus with binary data, most common. Hard real-time
		\item Modbus ASCII: Serial bus with ASCII. Just don't. Hard real-time
		\item Modbus TCP: Binary over TCP/IP. Not even soft real-time ensured
		\item Modbus over TCP: Slight differences to Modbus TCP, not commonly used
		\item Modbus UDP: Not commonly used
		\item Modbus Plus: Not commonly used
		\item Pemex Modbus: Not commonly used
		\item Enron Modbus: Not commonly used
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Which to use?}
	\centering
	\vfill
	You want to use Modbus TCP
	\vfill
\end{frame}

\begin{frame}
	\frametitle{What if I can't?}
	\centering
	\vfill
	If you have hard real-time requirements, you need to use Modbus RTU
	\vfill
	Create local islands of Modbus RTU where you need them
	\vfill
	Bridging into Modbus TCP is common and you can buy "master" units off the shelf
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Master \& slave}
	\centering
	\vfill
	References to master \& slave in modbus\_exporter have been removed even though they are still part of the official standard
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Addressing scheme}
	\begin{itemize}
		\item 00001-09999: Read-Write, Discrete Output Coils
		\item 10001-19999: Read-Only, Discrete Input Contacts
		\item 30001-39999: Read-Only, Analog Input Registers
		\item 40001-49999: Read-Write, Analog Output Holding Registers
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Addressing scheme}
	\begin{itemize}
		\item 00001-19999: Bit-wise addressing into a 2-byte block. So you need sub-addressing
		\item 30001-49999: 2-byte block. Unless you need 16 bits, you need suba-ddressing or combination
		\item You always get 2-byte blocks back so you need to do subadressing
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Wat?}
	\begin{itemize}
		\item No other data types defined
		\item Four ways to clobber a Float32 together:
		\begin{itemize}
			\item Big endian (1 2 3 4)
			\item Little endian (4 3 2 1)
			\item Mixed endian (2 1 4 3)
			\item YOLO endian (3 4 1 2)
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Waat?}
	\centering
	\vfill
	In Nomver 2019, I stated that at least I had not seen YOLO endian yet
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Waaat?}
	\centering
	\vfill
	I got email stating people had seen YOLO endian in the wild
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Waaaat?}
	\begin{itemize}
		\item Yes, "Input" and "Output" are from the perspective of the sender, not the actual device
		\item Yes, 50000+ is skipped in that spec; but you can use it
		\item Yes, the binary 0x0000 maps to decimal 00001
		\item No, there's no rule if you start counting with 0 or 1, it's free for all
		\item Addresses up to 65536, or 105536, are the "extended range". Not a problem as everyone is doing what they want, anyway.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Waaaaat?}
	\centering
	\vfill
	This standard is enforced by devices simply stopping to work
	\vfill
	Easy, reliable, horrible
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Reminder}
	\begin{itemize}
		\item Without Modbus, you would have no power
		\item Without Modbus, you would have no water
		\item Without Modbus, you would have no ports
		\item Without Modbus, you would have no medicine
		\item Without Modbus, you would have no processed food
		\item Without Modbus, you would have no clothes
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Maps}
	\centering
	\vfill
	Modbus maps are roughly what SNMP MIBs are
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Maps}
	\centering
	\vfill
	Only you can't unit test them and your production might stop working if you do something wrong
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Maps}
	\centering
	\vfill
	I have seen maps which are scans of photocopied paper
	\vfill
\end{frame}

\begin{frame}
	\frametitle{How do you work with that?}
	\centering
	\vfill
	Industry standard is to have a hex viewer, a map, an Excel sheet, and strong nerves
	\vfill
\end{frame}



\section{Datacenters}


\subsection{}

\begin{frame}
	\frametitle{What do I use this in datacenters for?}
	\centering
	\vfill
	Everything
	\vfill
\end{frame}

\begin{frame}
	\frametitle{What do I use this in datacenters for?}
	\centering
	\vfill
	Everything, except the cameras
	\vfill
\end{frame}


\begin{frame}
	\frametitle{What do I use this in datacenters for?}
	\centering
	\vfill
	Access control, intruder detection, glass breakage, fire detection, fire suppression, cooling set points, groundwater pump, groundwater filters, ion exchange pump, reverse osmosis system, water leakage, fan speed, doors opening and closing, fence gates, lighting, MCCB \& status, diesel engine status, diesel fuel tank levels, battery runtime, battery health, elevator access, elevator position, movement in secure areas, potential to ground, lightning strikes, microsecond events on power distribution, medium voltage, transformer load, transformer heat, floodlights, pressure release valves, airflow in office, temperature in office, temperature/humidity/pressure in data halls, smoke extraction fans, emergency exit status, LASER fence scanners, conductivity of cooling water\\
	Bullet-proof glass being shot at
	\vfill
\end{frame}

\begin{frame}
	\frametitle{What do I use this in datacenters for?}
	\centering
	\vfill
	Not a complete list
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Why?}
	\centering
	\vfill
	Why am I doing this?
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Why?}
	\centering
	\vfill
	I like pain
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Why?}
	\centering
	\vfill
	Modbus is the one standard supported by ALL industrial equipment
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Why?}
	\centering
	\vfill
	Modbus is horrible, but it's also extremely reliable within the constraints of its use
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Why?}
	\centering
	\vfill
	Because countless people would die if it wasn't
	\vfill
\end{frame}



\section{Prometheus}


\subsection{}

\begin{frame}
	\frametitle{How?}
	\centering
	\vfill
	\url{https://github.com/RichiH/modbus\_exporter}
	\vfill
	Max Inden did tons of work during a one-month networking \& Modbus stint at SpaceNet
	\vfill
	Needs more love, PRs and docs welcome
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Caveats}
	\centering
	\vfill
	If you have Modbus RTU, use a PLC as a gateway to expose Modbus TCP
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Caveats}
	\centering
	\vfill
	Reading out Modbus registers takes several seconds
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Future work}
	\centering
	\vfill
	Currently having my PLCs reprogrammed to expose seconds spent and might adapt exporter to calculate correct time
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Future work}
	\centering
	\vfill
	There is a semi-standard way to write a Modbus map and I want to have a generator like snmp\_exporter's
	\vfill
\end{frame}



\section{Outro}


\subsection{}

\begin{frame}
	\frametitle{Reminder}
	\begin{itemize}
		\item Without Modbus, you would have no power
		\item Without Modbus, you would have no water
		\item Without Modbus, you would have no ports
		\item Without Modbus, you would have no medicine
		\item Without Modbus, you would have no processed food
		\item Without Modbus, you would have no clothes
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Modbus}
	\centering
	\vfill
	Without Modbus, society would break down within hours
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Thanks!}
		\begin{center}
			\vfill
			Thanks for listening!
			\vfill
			Questions?
			\vfill
			Twitter: @TwitchiH
			\vfill
		\end{center}
\end{frame}

\end{document}

%\begin{frame}
%	\frametitle{}
%	\begin{itemize}
%		\item 
%		\item 
%		\item 
%		\item 
%		\item 
%	\end{itemize}
%\end{frame}
