\documentclass[t]{beamer}
\usepackage{helvet}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{Ilmenau}

\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}

\usepackage{units}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fixmath}
%\usepackage{pgfmath}
\usepackage{wrapfig}


\title{Prometheus @ Home}
%\subtitle{}
\author{Richard Hartmann,\\
RichiH@\{freenode,OFTC,IRCnet\},\\
richih@\{fosdem,debian,richih\}.org,\\
richard.hartmann@space.net}
\date{2017-08-18}


\begin{document}

% hide all subsections
\setcounter{tocdepth}{1}

%\section{Introduction}

%\subsection{}

\begin{frame}
	\titlepage
\end{frame}

%\subsection{}

%\begin{frame}
%	\frametitle{`whoami`}
%	\begin{itemize}
%		\item Richard "RichiH" Hartmann
%		\item System architect at SpaceNet
%		\item FOSDEM, DENOGx, PromCon staff
%		\item Prometheus team
%		\item Debian Developer
%		\item Author of \url{https://github.com/RichiH/vcsh}
%		\item Always looking for nice co-workers in the Munich area
%	\end{itemize}
%\end{frame}


%\section{Background}

%\subsection{}

\begin{frame}
	\frametitle{Pop quiz}
	\vfill
	\centerline{Did you know that it's near impossible to}
	\centerline{make backups of Prometheus data?}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Pop quiz}
	\vfill
	\centerline{(..no, I didn't know what Goutham would talk about..)}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Pop quiz}
	\vfill
	\centerline{So what happens if your home server dies}
	\centerline{and you don't have time to rebuild it?}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Pop quiz}
	\vfill
	\centerline{Did you expect pretty graphs?}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Pop quiz}
	\vfill
	\centerline{Well.. no.}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Actual content?}
	\vfill
	\centerline{I am here simply to whet your appetite.}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{OCD}
	\vfill
	\centerline{I get easily annoyed with inefficiency;}
	\centerline{if something works, I will use it in ALL the places}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{OCD}
	\vfill
	\centerline{(backups seem to be an exception)}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{OCD}
	\vfill
	\centerline{..same label printer}
	\centerline{..same screwdrivers}
	\centerline{..same keyboard \& mouse}
	\centerline{..same type of (colour-coded) notebook}
	\vfill
	\centerline{..and I flooded every place with literally 100+ pens of the same type}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Word of warning...}
	\vfill
	\centerline{..that includes having the}
	\centerline{same red Swingline stapler and home and at work}
	\vfill
\end{frame}


\begin{frame}
	\frametitle{Hmmmm...}
	\vfill
	\centerline{What if I could re-use Prometheus for useful and,}
	\centerline{more importantly, useless things?}
	\vfill
\end{frame}


\begin{frame}
	\frametitle{Home temperature, humidity, etc}
	\vfill
	\centerline{\url{github.com/prometheus/node_exporter}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home temperature, humidity, etc}
	\vfill
	\centerline{(..no, I didn't know what Nicolai would talk about..)}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home temperature, humidity, etc}
	\vfill
	\centerline{..but whatever, here you go:}
	\vfill
	\centerline{\url{github.com/vonneudeck/mouldy}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home automation}
	\vfill
	\centerline{\url{github.com/RichiH/knxd_exporter}}
	\vfill
	\centerline{Please write MOAR!}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home network}
	\vfill
	\centerline{\url{github.com/prometheus/snmp_exporter}}
	\vfill
	\centerline{\url{github.com/mdlayher/unifi_exporter}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home upstream; because those 2 Mbit/s are horrible}
	\vfill
	\centerline{\url{github.com/stefanwalther/speedtest-exporter}}
	\vfill
	\centerline{\url{github.com/RichiH/speedtest_exporter}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Home upstream; because those 2 Mbit/s are horrible}
	\vfill
	\centerline{Have you ever had some refuse your WiFi password?}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Gas prices}
	\vfill
	\centerline{\url{github.com/lukasmalkmus/tankerkoenig_exporter}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Weather data}
	\vfill
	\centerline{\url{github.com/RichiH/openweathermap_exporter}}
	\vfill
	\centerline{since February 2016}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Weather data}
	\vfill
	\centerline{I am soooo going to sue PromFlux}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Groundwater measurements}
	\vfill
	\centerline{\url{nid.bayern.de/grundwasser}}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Groundwater measurements}
	\vfill
	\centerline{Yes, I will correlate rain and groundwater}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Brian's special}
	\vfill
	\centerline{Have you ever argued with Brian?}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Brian's axiom}
	\vfill
	\centerline{"There is no use for weight or mass in a time series database"}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Brian's knowledge gap}
	\vfill
	\centerline{My co-workers have problems with stairs}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Brian's wrong}
	\vfill
	\centerline{USB scales exporting coffee grinder fill state}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{Brian's surprise}
	\vfill
	\centerline{..and alerting when it's empty}
	\vfill
\end{frame}

\begin{frame}
	\frametitle{RichiH's revenge}
	\vfill
	\centerline{..because it takes me less than ten seconds to reach the coffee grinder.}
	\vfill
\end{frame}



\end{document}

%\begin{frame}
%	\frametitle{}
%	\begin{itemize}
%		\item 
%		\item 
%		\item 
%		\item 
%		\item 
%	\end{itemize}
%\end{frame}
