%\documentclass[t]{beamer}
\documentclass[aspectratio=169]{beamer}
\usepackage{helvet}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{Ilmenau}

\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}

\usepackage{units}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fixmath}
%\usepackage{pgfmath}
\usepackage{wrapfig}


\title{Devroom opening}
\subtitle{}
\author{Richard Hartmann,\\
RichiH@\{freenode,OFTC,IRCnet\},\\
richih@\{debian,fosdem,richih\}.org,\\
@TwitchiH}
\date{2019-02-03}


\begin{document}

% hide all subsections
\setcounter{tocdepth}{1}

\section{Introduction}

\subsection{}

\begin{frame}
	\titlepage
\end{frame}

%\begin{frame}
%	\frametitle{Statistics}
%	\tableofcontents
%\end{frame}

\subsection{}

\begin{frame}
	\frametitle{Welcome}
	\begin{center}
		\vfill
		Welcome to our third monitoring devroom in a row!
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thanks!}
	\begin{center}
		\vfill
		Ben Kochie
		\vfill
		Carl Bergquist
		\vfill
		Fabian Staeder
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Rosario Antoci
		\vfill
		What's new in Zabbix 4.0?
		\vfill
		Zabbix is one of the most powerful traditional monitoring systems and it helped kept sane over almost a decade.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Simone Mainardi
		\vfill
		Augmented Network Visibility with High-Resolution Metrics
		\vfill
		Bursts are bad, and unless you see them, you will have a bad time.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Jaana Dogan
		\vfill
		Critical Path Analysis
		\vfill
		There are only a few useful ways to think about observability, this is one of them.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Richard Hartmann
		\vfill
		On Observability
		\vfill
		This is a different way to think about observability.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Tom Wilkie
		\vfill
		Loki - Prometheus for logs
		\vfill
		What if we had good metadata on logs? Would that scale?
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Heinrich Hartmann
		\vfill
		Latency SLOs done right
		\vfill
		So you know what you want to observe, but where do you draw the line?
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Rob Skillington
		\vfill
		M3 and a new age of metrics and monitoring in an increasingly complex world
		\vfill
		Uber for metrics
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Iain Learmonth
		\vfill
		Privacy-preserving monitoring of an anonymity network
		\vfill
		Making the world a freer place, but still need monitoring...
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Peter Zaitsev
		\vfill
		Using eBPF for Linux Performance Analyses
		\vfill
		New ways to extract data out of Linux systems.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Bartek Plotka
		\vfill
		Thanos - Transforming Prometheus to a Global Scale in a Seven Simple Steps
		\vfill
		Prometheus backed by object storage.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Matthias Loibl, Sergiusz Urbaniak
		\vfill
		Deep Dive: Kubernetes Metrics with Prometheus
		\vfill
		You can't run Kubernetes without a good observability story, and this might be the best.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		James Shubin
		\vfill
		Real-time merging of config management and monitoring
		\vfill
		On the path to self-healing systems.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Hannah Suarez
		\vfill
		Let's use centralized log collection to make incident response teams happy
		\vfill
		Having one source of truth is good.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Ilya Etingof
		\vfill
		Writing Asynchronous SNMP Agents
		\vfill
		You like pain? This is pain.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Konstantin Mikhaylov
		\vfill
		SAYMON - object-oriented monitoring and management for both ICT and IoT
		\vfill
		Monitoring of things.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		Michael Ströder
		\vfill
		slapdcheck
		\vfill
		Making sure your stuff auth base is clean and working.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Rules}
	\begin{center}
		\vfill
		Take all trash with you, no matter if yours or not.
		\vfill
		Use the trashcan to the back.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Respect}
	\begin{center}
		\vfill
		Speakers do this for free.
		\vfill
		To maximize Q\&A time we will allow you to leave \& enter during the Q\&A.
		\vfill
		Leave and enter quietly or we WILL shout you down.
		\vfill
	\end{center}
\end{frame}

%%%%%%%%%%%% be nice, or....

%%% trashcans to the back

\end{document}

%\begin{frame}
%	\frametitle{}
%	\begin{itemize}
%		\item 
%		\item 
%		\item 
%		\item 
%		\item 
%	\end{itemize}
%\end{frame}
