%\documentclass[t]{beamer}
\documentclass[aspectratio=169]{beamer}
\usepackage{helvet}
\usepackage{calc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usetheme{Ilmenau}

\setbeamercovered{transparent}
\setbeamertemplate{navigation symbols}{}

\usepackage{units}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fixmath}
%\usepackage{pgfmath}
\usepackage{wrapfig}


\title{Devroom opening}
\subtitle{}
\author{Richard Hartmann,\\
RichiH@\{freenode,OFTC,IRCnet\},\\
richih@\{debian,fosdem,richih\}.org,\\
@TwitchiH}
\date{2020-02-01}


\begin{document}

% hide all subsections
\setcounter{tocdepth}{1}

\section{Introduction}

\subsection{}

\begin{frame}
	\titlepage
\end{frame}

%\begin{frame}
%	\frametitle{Statistics}
%	\tableofcontents
%\end{frame}

\subsection{}

\begin{frame}
	\frametitle{Welcome}
	\begin{center}
		\vfill
		Welcome to our fourth monitoring devroom in a row!
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Thanks!}
	\begin{center}
		\vfill
		Ben Kochie
		\vfill
		Brian Brazil
		\vfill
		Carl Bergquist
		\vfill
		Fabian Staeber
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{20 years...}
	\begin{center}
		\vfill
		20 years of FOSDEM
		\vfill
		Time for reflection
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Reflection}
	\begin{center}
		\vfill
		Four times in a row...
		\vfill
		Seven, in total, is top list territory!
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Full disclosure}
	\begin{center}
		\vfill
		I am FOSDEM staff, but have never done devroom selection/coordination
		\vfill
		...don't even know how they are selected
		\vfill
		...so I am not voting for or influencing the selection process in any way
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Content}
	\begin{center}
		\vfill
		CfP selection was done blindly
		\vfill
		Still massive representation from Red Hat and Grafana
		\vfill
		This shows company strategy, but also that more people should submit interesting stuff
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Diversity}
	\begin{center}
		\vfill
		Reminder: We offer training, feedback, help for diversity speakers
		\vfill
		No travel sponsorship as this is all done by volunteers
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{On a personal note}
	\begin{center}
		\vfill
		Another full disclosure
		\vfill
		I joined Grafana as Director, Community
		\vfill
		Will be super interesting
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Looking ahead}
	\begin{center}
		\vfill
		Tracing is still gathering steam
		\vfill
		Refelected in talk selection
		\vfill
		First three talks are tracing-only
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Rest of the content}
	\begin{center}
		\vfill
		Rest split up into Deep, Genereal, Fun in a cycle, ending with general content
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Looking further ahead}
	\begin{center}
		\vfill
		There's talk about going back to monoliths for some workloads
		\vfill
		There's talk about getting nearer to metal again
		\vfill
		There's talk about putting storage and compute closer together and not offloading to the network
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Looking further ahead}
	\begin{center}
		\vfill
		This will impact the observability space
		\vfill
		Things will remain fun!
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Rules}
	\begin{center}
		\vfill
		Take all trash with you, no matter if yours or not.
		\vfill
		Use the trashcan to the back.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Respect}
	\begin{center}
		\vfill
		Speakers do this for free.
		\vfill
		To maximize Q\&A time we will allow you to leave \& enter during the Q\&A.
		\vfill
		Leave and enter quietly or we WILL shout you down.
		\vfill
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Fun}
	\begin{center}
		\vfill
		Have fun!
		\vfill
		I know we do
		\vfill
	\end{center}
\end{frame}

%%%%%%%%%%%% be nice, or....

%%% trashcans to the back

\end{document}

%\begin{frame}
%	\frametitle{}
%	\begin{itemize}
%		\item 
%		\item 
%		\item 
%		\item 
%		\item 
%	\end{itemize}
%\end{frame}
